Draft

### 2022-06-30 ms.tex
ms0629

\newcommand{\Msun}{\mathrm{M_\odot}}
\newcommand{\Msunyr}{\mathrm{M_\odot~yr^{-1}}}
\newcommand{\Mh}{M_\mathrm{h}}
\newcommand{\Mseed}{M_\mathrm{seed}}
\newcommand{\zseed}{z_\mathrm{seed}}
\newcommand{\hh}{\mathrm{H_2}}
\newcommand{\CII}{\mathrm{C_{II}}}
\newcommand{\vbsm}{v_\mathrm{bsm}}
\newcommand{\jlw}{J_{\rm LW}}
\newcommand{\Mdot}{\dot{M}}
\newcommand{\tlife}{t_\mathrm{life}}
\newcommand{\fseed}{f_\mathrm{seed}}
\newcommand{\fobsc}{f_\mathrm{obsc}}
\newcommand{\tEdd}{t_\mathrm{Edd}}
\newcommand{\Nt}{N_\mathrm{t}}
\newcommand{\Muv}{M_{1450}}
\newcommand{\Lbol}{L_\mathrm{bol}}
\newcommand{\fbol}{f_\mathrm{bol}}
\newcommand{\D}{\mathrm{d}}

@@

@@

\shorttitle{BH growth toward $z=$ 6 BHMF \& QLF}
\shortauthors{Li et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
% \watermark{DRAFT}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%% \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{{../figs/}}
% \graphicspath{{./}{figures/}{figs/}}
%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

@@

%%%%%%%%%
%	REVISE.   %
%%%%%%%%%
\red{KI: we need to explain how we calculate the final stellar mass from the accretion rate. pls add one new paragraph here. 
also add an argument about translation from stellar mass to BH remnant mass.}

Zooming in to the protostellar vicinity, an accretion disk forms due to the angular momentum of the inflowing material from large scale. 
The episodic accretion through the clumpy disk decreases the time-averaged accretion rate onto the protostar by $\Mdot_{\star}=\eta \Mdot$, 
where we take $\eta=0.3$ as the conversion efficiency from global accretion to that through the disk \citep[][Toyouchi 2022]{2016MNRAS.459.1137S}. 
\blue{
  (Toyouchi+ find 0.4 actually.)
}
We then exploit the accretion rate to estimate the protostellar mass and that of the subsequent seed BH formed.

The growth pattern of an accreting protostar differs in the effect of radiative feedback,
with the accretion rate $\Mdot_\star$ in different regimes compared with a critical value $\dot{M}_{\mathrm{crit}}=0.04~\Msunyr$ 
\citep{2001ApJ...561L..55O,2013ApJ...778..178H,2013A&A...558A..59S,2015MNRAS.452..755S,2018MNRAS.474.2757H}.
With average accretion rates exceeding $\Mdot_\mathrm{crit}$, the stellar envelope inflates, 
with its surface temperature as low as $T_\mathrm{eff} \simeq 5000$ K, 
resulting in trivial UV radiative feedback that hardly affect the accretion flow. 
The stellar mass is then built up to $\sim 10^5~\Msun$ and limited by the internal GR instability 
\citep{2016PhRvD..94b1501S,2017ApJ...842L...6W,2019PASA...36...27W}, which is fitted as 
\begin{equation*}
 M_{\star, \mathrm{GR}} \simeq\left[0.83 \log \left(\frac{\dot{M}_{\star}}{\Msunyr}\right)+2.48\right] \times 10^{5} ~\Msun,
\end{equation*}
in the range of $\dot{M}_\star\gtrsim 0.1~\Msunyr$.

On the other hand, with accretion rates lower than $\Mdot_\mathrm{crit}$, 
protostars can contract with the effective temperature rapidly increasing to $\sim 10^5$ K, 
hence the strong UV photons photoevaporate the gaseous disk and hinder the mass accretion 
\citep{2008ApJ...681..771M,2011Sci...334.1250H}. 
In this case, the final stellar mass is capped by the balance of the mass loss rate via disk photoevaporation $\dot{M}_{\mathrm{pe}}$
and the accretion rate $\dot{M}_{\star}$, and the former is expressed as 
% \begin{equation*}
  % \dot{M}_{\mathrm{pe}} \simeq 2.1 \times 10^{-2} \Msunyr \left(\frac{\Phi_{\mathrm{ion}}}{10^{52} \mathrm{~s}^{-1}}\right)^{1 / 2}\left(\frac{R_{\rm{disk}}}{0.1 \mathrm{pc}}\right)^{1/2}.
% \end{equation*}
$\dot{M}_{\mathrm{pe}} \simeq 2.1 \times 10^{-2} \Msunyr \left( \Phi_{\mathrm{ion}}/10^{52} \mathrm{~s}^{-1}\right)^{1 / 2}\left(R_{\rm{disk}}/0.1 \mathrm{pc}\right)^{1/2}$ 
\citep{2013ApJ...773..155T}.
Here we adopt the emissivity of UV photons $\Phi_{\mathrm{ion}} \simeq 1.6 \times 10^{52} \mathrm{~s}^{-1}\left(M_{\star} / 10^{4} \Msun \right)$ following \citet{2012ApJ...750...66J}, 
and the disk size is estimated as the stellar gravitational influence radius for 2$\times 10^4$ K ionized gas 
$R_{\mathrm{disk}} \simeq  G M_{\star}/c_{\mathrm{s}, \mathrm{ion}}^{2} \simeq 0.17 \mathrm{pc}\left( M_{\star}/ 10^{4} \Msun \right)$.
The final stellar mass regulated by radiative feedback is thus 
\begin{equation*}
M_{\star, \mathrm{fb}} \simeq 2.9 \times 10^{3} \Msun\left(\frac{\dot{M}_{\star}}{0.01 M_{\odot} \mathrm{yr}^{-1}}\right), 
\end{equation*}
for $\Mdot_\star\lesssim \Mdot_\mathrm{crit}$.

With the intermediate accretion rates between $\Mdot_\mathrm{crit}$ and $0.1~\Msunyr$, 
we perform logarithmic interpolation in the $\Mdot_\star - M_\star$ plane to smoothly connect 
$M_{\star, \mathrm{fb}}$ and $M_{\star, \mathrm{GR}}$ at the boundaries.
In the death of these metal poor stars, most mass are expected to reserve to the collapse into BHs 
\citep{2003ApJ...591..288H,2010ApJ...714.1217B,2015MNRAS.451.4086S}.
Therefore, we take the seed BH masses as those of their progenitor stars.

Based on the probability distribution function of the BH seed mass $\D P/ \D \log M_{\bullet, i}$, we construct the mass function of those seeds formed in one parent halo
with a mass of $\Mh$ where gas has a coherent streaming velocity of $\vbsm$ as a function of time (and redshift).
The absolute abundance of those seed BHs is calculated with the number density of the parent halo in a comoving volume at $z=6$ 
from the Sheth-Tormen mass function \citep{2001MNRAS.323....1S},
%
\begin{align}
  n_{\Mh}= \int_{\Mh}^{10\Mh}  \frac{\D n_{\mathrm{ST}}} {\D \Mh'} \D \Mh', 
\end{align}
%
where we adopt $\Mh = 10^{11}$, $10^{12}$, and $10^{13}~\Msun$, 
% (\red{KI: explicitly show those numbers?})
with number densities $n_{\Mh} = 9.87\times 10^{-4}$, $6.15\times 10^{-6}$, 
and $8.92\times 10^{-10}~ \text{Mpc}^{-3}$, respectively.
Combining the PDF and number normalization, we obtain the seed BH mass function as
%
\begin{align}
\Phi_\mathrm{M}^{\rm seed} \equiv \sum_{\Mh, \vbsm} n_{\Mh} f_{\vbsm} 
\cdot \frac{\D P}{\D \log M_{\bullet, i}}\Big| _{\Mh, \vbsm},
\end{align}
%
where $f_{\vbsm}$ is the volume fraction of the universe with a streaming velocity.
The value is calculated as $f_{\vbsm} = 0.6$ and $0.4$ for $\vbsm = 0$ and $\vbsm=1~\sigma_{\rm bsm}$, respectively.

@@

%%%%%%%
%    Fig. 2
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=170mm]{scheme.pdf}
\caption{
Schematical demonstration of the procedure to calculate the evolution of BH mass distribution 
from time $t$ to $t+\Delta t$. 
The probability of a BH with mass $M_\mathrm{i}$ grow to $M$ after $\Delta t$ is drew from the 
ERDF following Eq.~\ref{eq:Pl}. 
Thus the new BH mass distribution is reshaped iteratively by integrating with the ERDF. 
}
\label{fig:scheme}
\vspace{5mm}
\end{figure*}

% Figure 1 shows the BH seeds formed in progenitors of $\Mh = 10^{11}, 10^{12}$
\vspace{2mm}
\subsection{BH mass growth}
% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. 
% We have constraints on simulations and observations of lower redshift counterparts.
With BH seeds planted, we grow the BHs with a semi-analytical accretion rate model and study the evolution of the BH mass distribution until $z=6$. 
\blue{(references + discussion)}
The growth model is characterized by a minimal number of free parameters, 
% the quasar accretion is episodic with Eddington ratio variations,
describing the BH mass growth rate $\Mdot$ by
%%%%%%%
%    Eq. 1
%%%%%%%
% \begin{equation*}
%   \label{eq:mdot_1}
%   \Mdot_\bullet = \frac{\lambda f(M_\bullet) M_\bullet}{\tEdd} ,
% \end{equation*}
\begin{equation}
  \label{eq:mdot}
  \Mdot_\bullet = \lambda f(M_\bullet) \Mdot_\mathrm{Edd} ,
\end{equation}
% where $\tEdd = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
where $\lambda \equiv L/L_\mathrm{Edd}$ is the Eddington ratio,
and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a 10\% radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
%Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $,
%according to the thin accretion disk model \citep{1973A&A....24..337S}, 
which is consistent with the value obtained from the Soltan's argument \citep{1982MNRAS.200..115S,2002MNRAS.335..965Y}.
% The high mass BH should be strangulated by as it grows, 
We define the mass dependent function of $f(M_\bullet)$ as 
%
\begin{equation}
f(M_\bullet) = \frac{2}{1+\left(M_\bullet /M_{\bullet,c} \right)^\delta}, 
\end{equation}
%
where we adopt $M_{\bullet,c}=10^8~\Msun$.
With a positive value of $\delta$, the BH growth at the high mass end is suppressed. \blue{(references, Ueda+14?s)}.
In the limit of $\delta \ll 1$, where $f(M_\bullet) \simeq 1$ is approximated independent of $M_{\bullet,c}$, the model reproduces an exponential growth with an $e$-folding timescale of
$\tEdd =  M_\bullet/\Mdot_{\mathrm{Edd}} \approx 45$ Myr.
%h independent of BH mass.
% In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.
%Then $\tEdd =  M/\Mdot_{\mathrm{Edd}} \approx 45$ Myr is the Salpeter $e$-folding timescale \citep{1964ApJ...140..796S}.

The quasar activity is episodic in nature, with accretion bursts triggered by gas inflows to the galactic nuclei
% \citep[e.g., mergers or disk instabilities, see][]{2005Natur.433..604D,2005ApJ...630..705H}, 
\citep{2005Natur.433..604D,2005ApJ...630..705H}, 
and the accretion rate declines with self-regulating feedbacks \citep[e.g.,][]{2008ApJ...686..815Y,2011ApJ...737...26N} or 
self-similar disk evolution \citep{1991MNRAS.248..754P,2005ApJ...634..901Y,2007MNRAS.377L..25K}. \red{KI: what's this?}
This ``flickering'' pattern of individual quasar luminosity evolution can be directly translated into the diversity in the Eddington ratios of a quasar sample, 
\red{where the Eddington ratio distribution function (ERDF) $\D P/ \D\ln\lambda$ shares the same Schechter function shape 
with the differential time at different $\lambda$ \citep{2006ApJ...639..700H,2009ApJ...698.1550H}.}
\red{KI: don't follow this logic...}
For type-I AGN populations at low redshifts, the ERDF is characterized with a Schechter function
%Observations also propose that the intrinsic ERDF in lower-$z$ quasars hosted by star forming galaxies follows a Schechter shape, 
\citep{2015MNRAS.447.2085S,2016ApJ...826...12J,2018MNRAS.474.1225A}.
Motivated by those facts, we give the ERDF by a Schechter function with two free parameters $\lambda_0$ and $\alpha$ as
%%%%%%%
%    Eq. 2
%%%%%%%
\begin{equation}
  \label{eq:Pl}
  \frac{\D P}{ \D \ln \lambda} \propto
  \left(\frac{\lambda} {\lambda_0} \right)^\alpha \exp{\left(-\frac{\lambda}{\lambda_0}\right)}.
\end{equation}
The normalization is set so that the integrant of this function over $\lambda_\mathrm{min}(=0.01) \leq \lambda < \infty$ is unity.
%normalized by the total probability above $\lambda_\mathrm{min}$ = 0.01.
The minimum Eddington ratio $\lambda_\mathrm{min}$ is adopted from the simulated evolution of quasar luminosities 
that decrease mildly toward $\lambda \sim 0.1-0.01$ with $\lesssim$ 100 Myr after the peak activity \citep{2011ApJ...737...26N}.
Moreover, a turnover at the lowest value $\lambda\lesssim 0.01-0.001$ in the ERDF is suggested by observations \citep{2018MNRAS.474.1225A}.

To characterize the ERDF for a BH population at any time snapshot together with the episodic accretion pattern of individual BHs, 
we introduce a time duration of $\tlife$, during which a single value of $\lambda$ that follows the ERDF of Eq.~(\ref{eq:Pl}) is assigned to an accreting BH.
In this way, we give a different growth speed of a BH in every period with a duration of $\tlife$ until $z=6$ (the corresponding cosmic age is $t_{\rm H}\simeq 800$ Myr).
This treatment enables us to capture the nature of accretion bursts and avoid an unrealistically long-lasting rapid growth phase of a BH.
\red{We note that the value of $\tlife$ is indispensable as a methodology in our modeling, 
albeit its direct comparison with observational luminous quasar lifetime is difficult, 
these timescales are correlated in realizing the SMBH growth. 
We leave a more detailed discussion to \S~\ref{sec:discussion}.}
To be done later...

@@

We describe how to calculate the time evolution of the BH mass function, combining the semi-analytical growth model 
and the ERDF (see Eqs.~\ref{eq:mdot} and \ref{eq:Pl}).
For a given mass distribution function $\D P/\D  M_{\bullet, i}$ at $t=t_i$, we give the BHMF at $t=t_i+\Delta t$ as
%%%%%%%
%    Eq. 5
%%%%%%%
\begin{equation}
  \label{eq:dpdm}
  \frac{\D P}{\D M_\bullet} = \int
   \frac{\D P}{\D \ln \lambda}\Big|_{\lambda_\ast} \cdot
   \frac{\D \ln \lambda_\ast}{\D  M_\bullet}\Big|_{\Delta t, M_{\bullet,i}} \cdot
   %_{M, M_\mathrm{i},\Delta t, \delta}
  \frac{\D P}{\D M_{\bullet, i}}~\D M_{\bullet, i},
\end{equation}
%
where $\lambda_\ast$ is the Eddington ratio required for a BH with $M_{\bullet,i}$ to grow up to $M_{\bullet}$ within $\Delta t$
and is calculated analytically by
%%%%%%%
%    Eq. 4
%%%%%%%
\begin{equation}
  \label{eq:mi2m}
\frac{\lambda_\ast \Delta t}{\tEdd}=
  \ln \left(\frac{M_\bullet} {M_{\bullet,i}}\right) + \frac{1}{\delta} 
  \left[ \left(\frac{M_\bullet}{M_{\bullet,c}}\right)^\delta - \left(\frac{M_{\bullet, i}}{M_{\bullet,c}}\right)^\delta \right],
\end{equation}
%
and the derivative of ($\D \ln \lambda_\ast / \D  M_\bullet )|_{\Delta t, M_{\bullet,i}}$ is given by Eq.~(\ref{eq:mi2m}).
After the seed formation terminates (i.e., after the total number of BHs is fixed), we perform this integration in every timestep 
by setting to $\Delta t = t_{\rm life}$ until $z=6$.

>>>>

\newcommand{\Msun}{M_\odot}
\newcommand{\Msunyr}{M_\odot~{\rm yr}^{-1}}
\newcommand{\Mh}{M_\mathrm{h}}
\newcommand{\Mseed}{M_\mathrm{seed}}
\newcommand{\zseed}{z_\mathrm{seed}}
\newcommand{\hh}{\mathrm{H_2}}
\newcommand{\CII}{\mathrm{C_{II}}}
\newcommand{\vbsm}{v_\mathrm{bsm}}
\newcommand{\jlw}{J_{\rm LW}}
\newcommand{\Mdot}{\dot{M}}
% \newcommand{\tlife}{t_\mathrm{life}}
\newcommand{\tlife}{\tau}
\newcommand{\fseed}{f_\mathrm{seed}}
\newcommand{\fobsc}{f_\mathrm{obsc}}
\newcommand{\tEdd}{t_\mathrm{Edd}}
\newcommand{\Nt}{N_\mathrm{t}}
\newcommand{\Muv}{M_{1450}}
\newcommand{\Lbol}{L_\mathrm{bol}}
\newcommand{\fbol}{f_\mathrm{bol}}
\newcommand{\D}{\mathrm{d}}

@@

\defcitealias{2010AJ....140..546W}{W10}
\defcitealias{2018ApJ...869..150M}{M18}

@@

\shorttitle{BH growth toward $z=$ 6 BHMF \& QLF}
 \shortauthors{Li et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
% \watermark{DRAFT}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%% \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{{./}{../figs/}}
% \graphicspath{{./}{figures/}{figs/}}
%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

@@

At the vicinity of an accreting protostar, an accretion disk forms due to angular momentum of the inflowing material from large scales. 
The episodic nature of disk accretion decreases the time-averaged accretion rate onto the protostar as $\Mdot_{\star}=\eta \Mdot$, 
where we adopt $\eta=0.3$ as the conversion efficiency \citep[][Toyouchi 2022]{2016MNRAS.459.1137S}. 
%\blue{
%  (Toyouchi+ find 0.4 actually.)
%}
%Thus, we estimate the accretion rate to estimate the protostellar mass and that of the subsequent seed BH formed. 
The stellar radius evolution of an accreting protostar and the radiative feedback strength depend sensitively on whether
the accretion rate becomes higher than a critical value of $\dot{M}_{\mathrm{crit}}=0.04~\Msunyr$ 
\citep{2001ApJ...561L..55O,2013ApJ...778..178H,2013A&A...558A..59S,2015MNRAS.452..755S,2018MNRAS.474.2757H}.
For $\dot{M}_\ast > \Mdot_\mathrm{crit}$, the stellar envelope inflates owing to rapid entropy injection through accreting matter,
keeping its surface temperature as low as $T_\mathrm{eff} \simeq 5000$ K. 
Since stellar UV radiation is hardly emitted from the cold surface, the accretion flow efficiently feeds the central star without being 
impeded by radiative feedback.
As a result, the stellar mass reaches $\sim 10^5~\Msun$ but is limited by the general-relativistic instability to
%
\begin{equation}
 M_{\star, \mathrm{GR}} \simeq\left[0.83~\log \left(\frac{\dot{M}_{\star}}{\Msunyr}\right)+2.48\right] \times 10^{5} ~\Msun,
\end{equation}
%
in the range of $\dot{M}_\star\gtrsim 0.1~\Msunyr$ \citep{2016PhRvD..94b1501S,2017ApJ...842L...6W,2019PASA...36...27W}.
On the other hand, for $\dot{M}_\ast \leq \Mdot_\mathrm{crit}$, protostars can contract by loosing its thermal energy via radiative diffusion
and increases its surface temperature to $T_\mathrm{eff} \sim 10^5$ K.
Hence, intense stellar UV radiation heats the disk surface and launches mass outflows, preventing mass supply from the disk to the star
\citep{2008ApJ...681..771M,2011Sci...334.1250H}. 
In this case, the stellar mass is determined by the balance between mass accretion and mass loss via photoevaporation \citep{2013ApJ...773..155T},
and can be approximated as (see more details in \citealt{2021ApJ...917...60L})
%the final stellar mass is capped by the balance of the mass loss rate via disk photoevaporation $\dot{M}_{\mathrm{pe}}$
%and the accretion rate $\dot{M}_{\star}$, and the former is expressed as 
% \begin{equation*}
  % \dot{M}_{\mathrm{pe}} \simeq 2.1 \times 10^{-2} \Msunyr \left(\frac{\Phi_{\mathrm{ion}}}{10^{52} \mathrm{~s}^{-1}}\right)^{1 / 2}\left(\frac{R_{\rm{disk}}}{0.1 \mathrm{pc}}\right)^{1/2}.
% \end{equation*}
%$\dot{M}_{\mathrm{pe}} \simeq 2.1 \times 10^{-2} \Msunyr \left( \Phi_{\mathrm{ion}}/10^{52} \mathrm{~s}^{-1}\right)^{1 / 2}\left(R_{\rm{disk}}/0.1 \mathrm{pc}\right)^{1/2}$ 
%\citep{2013ApJ...773..155T}.
%Here we adopt the emissivity of UV photons $\Phi_{\mathrm{ion}} \simeq 1.6 \times 10^{52} \mathrm{~s}^{-1}\left(M_{\star} / 10^{4} \Msun \right)$ following \citet{2012ApJ...750...66J}, 
%and the disk size is estimated as the stellar gravitational influence radius for 2$\times 10^4$ K ionized gas 
%$R_{\mathrm{disk}} \simeq  G M_{\star}/c_{\mathrm{s}, \mathrm{ion}}^{2} \simeq 0.17 \mathrm{pc}\left( M_{\star}/ 10^{4} \Msun \right)$.
%The final stellar mass regulated by radiative feedback is thus 
%
\begin{equation}
M_{\star, \mathrm{fb}} \simeq 2.9 \times 10^{3} \Msun\left(\frac{\dot{M}_{\star}}{0.01 M_{\odot} \mathrm{yr}^{-1}}\right).
\end{equation}
%
%for $\Mdot_\star\lesssim \Mdot_\mathrm{crit}$. 
For an intermediate accretion rate between $\Mdot_\mathrm{crit}$ and $0.1~\Msunyr$, 
we perform logarithmic interpolation in the $\Mdot_\star - M_\star$ plane to smoothly connect 
$M_{\star, \mathrm{fb}}$ and $M_{\star, \mathrm{GR}}$ at the boundaries.
At the end of the stellar lifetime, those massive primordial stars result in BHs without significant mass loss via stellar winds.
\citep{2003ApJ...591..288H,2010ApJ...714.1217B,2015MNRAS.451.4086S}.
Therefore, we consider the mass distribution of seed BHs as that of their stellar progenitors.

\blue{
  I think the $\Phi^{\rm seed}$ is accurate with the following descriptions, also used for Sec. 2.3
}
In the $itr$-th DM growth history where a seed BH is formed with mass $M_\text{itr}$ at the cosmic age $t_\text{itr}$, 
it discretely contributes to the probability distribution function of seed mass at time $t$ as 
\begin{equation}
  p^{\rm seed}_{\rm itr} (M_\bullet,t)\equiv \frac{\D^2 P^{\rm seed}_{\rm itr}}{\D M_\bullet \D t}= 10^{-4} \delta(M_\bullet-M_\text{itr}) \delta(t-t_\text{itr}).
\end{equation}
Based on the cumulative seed mass probability distribution function $\D P^{\rm seed}_{\rm itr}/ \D M_{\bullet} \left(t\right)$ 
which is the integral of $p^{\rm seed}_{\rm itr} (M_\bullet,t)$ over time, 
we construct the mass function from all seeds ($itr$ from 1 to 10$^4$) formed in one parent halo
with a mass of $\Mh$ where gas has a coherent streaming velocity of $\vbsm$ as a function of time (and redshift).
The absolute abundance of those seed BHs is calculated with the number density of the parent halo in a comoving volume at $z=6$ 
from the Sheth-Tormen mass function \citep{2001MNRAS.323....1S},
%
\begin{align}
  n_{\Mh}= \int_{\Mh}^{10\Mh}  \frac{\D n_{\mathrm{ST}}} {\D \Mh'} \D \Mh', 
\end{align}
%
where we adopt $\Mh = 10^{11}$, $10^{12}$, and $10^{13}~\Msun$, with number densities of
$n_{\Mh} = 9.9\times 10^{-4}$, $6.2\times 10^{-6}$, and $8.9\times 10^{-10}~ \text{Mpc}^{-3}$, respectively.
Combining the PDF and number density normalization, we obtain the seed BH mass function cumulative at time $t$ as
%
\begin{align}
\Phi_{M_\bullet}^{\rm seed}\left(t\right) \equiv \sum_{\Mh, \vbsm} n_{\Mh} f_{\vbsm} 
\cdot \sum_{\rm itr} \frac{\D P_{\rm itr}^{\rm seed}}{\D \log M_{\bullet}}\left(t\right) \Big| _{\Mh, \vbsm},
\end{align}
%
where $f_{\vbsm}$ is the volume fraction of the universe with a streaming velocity.
The value is calculated as $f_{\vbsm} = 0.6$ and $0.4$ for $\vbsm = 0$ and $\vbsm=1~\sigma_{\rm bsm}$, respectively.

@@

%%%%%%%
%    Fig. 2
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=150mm]{scheme.png}
\caption{
Schematical demonstration of the procedure to calculate the evolution of BH mass distribution 
between checkpoints time $t_0$ to $t_0+\tau$. 
The probability of a BH with mass $M_0$ grow to $M$ after $\Delta t=\tau$ is drew from the 
ERDF following Eq.~\ref{eq:Pl}. 
For a newly formed seed BH $M_{\rm i}$, the probability distribution function of BH mass is a delta function, 
and the growth time is $t_0+\tau-t_{\rm i}$.
Thus the evolution of BH mass distribution is reshaped iteratively 
plus taking account of the newly formed seeds if any.
}
\label{fig:scheme}
\vspace{5mm}
\end{figure*}

% Figure 1 shows the BH seeds formed in progenitors of $\Mh = 10^{11}, 10^{12}$
\vspace{2mm}

\subsection{BH mass growth}
% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. 
% We have constraints on simulations and observations of lower redshift counterparts.
With BH seeds planted, we grow the BHs with a semi-analytical accretion rate model and study the evolution of the BH mass distribution until $z=6$. 
\blue{(references + discussion)}
The growth model is characterized by a minimal number of free parameters, 
% the quasar accretion is episodic with Eddington ratio variations,
describing the BH mass growth rate $\Mdot$ by
%%%%%%%
%    Eq. 1
%%%%%%%
% \begin{equation*}
%   \label{eq:mdot_1}
%   \Mdot_\bullet = \frac{\lambda f(M_\bullet) M_\bullet}{\tEdd} ,
% \end{equation*}
\begin{equation}
  \label{eq:mdot}
  \Mdot_\bullet = \lambda f(M_\bullet) \Mdot_\mathrm{Edd} ,
\end{equation}
% where $\tEdd = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
where $\lambda \equiv L/L_\mathrm{Edd}$ is the Eddington ratio,
and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a 10\% radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
%Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $,
%according to the thin accretion disk model \citep{1973A&A....24..337S}, 
which is consistent with the value obtained from the Soltan's argument \citep{1982MNRAS.200..115S,2002MNRAS.335..965Y}.
% The high mass BH should be strangulated by as it grows, 
We define the mass dependent function of $f(M_\bullet)$ as 
%
\begin{equation}
f(M_\bullet) = \frac{2}{1+\left(M_\bullet /M_{\bullet,c} \right)^\delta}, 
\end{equation}
%
where we adopt $M_{\bullet,c}=10^8~\Msun$.
With a positive value of $\delta$, the BH growth at the high mass end is suppressed. \blue{(references, Ueda+14?s)}.
In the limit of $\delta \ll 1$, where $f(M_\bullet) \simeq 1$ is approximated independent of $M_{\bullet,c}$, the model reproduces an exponential growth with an $e$-folding timescale of
$\tEdd =  M_\bullet/\Mdot_{\mathrm{Edd}} \approx 45$ Myr.
%h independent of BH mass.
% In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.
%Then $\tEdd =  M/\Mdot_{\mathrm{Edd}} \approx 45$ Myr is the Salpeter $e$-folding timescale \citep{1964ApJ...140..796S}.

The quasar activity is episodic in nature, with accretion bursts triggered by gas inflows to the galactic nuclei
% \citep[e.g., mergers or disk instabilities, see][]{2005Natur.433..604D,2005ApJ...630..705H}, 
\citep{2005Natur.433..604D,2005ApJ...630..705H}, 
and the accretion rate declines by self-regulating feedback processes \citep[e.g.,][]{2008ApJ...686..815Y,2011ApJ...737...26N} 
or gas consumption \citep{1991MNRAS.248..754P,2005ApJ...634..901Y,2007MNRAS.377L..25K}. 
This ``flickering'' pattern of individual quasar luminosity evolution can be directly translated into the diversity 
in the Eddington ratios of quasar samples. 
We here suppose that the Eddington ratio distribution function $\D P/ \D\ln\lambda$ (ERDF) is characterized
with a Schechter function and the distribution function is independent of redshift 
\citep{2006ApJ...639..700H,2009ApJ...698.1550H}. \red{KI: I slightly modified the previous sentence. Is that what you meant?}
\blue{
  not exactly, what I meant may not be necessary here, but we may discuss later.
}
For type-I AGN populations at low redshifts, the ERDF is characterized with a Schechter function
%Observations also propose that the intrinsic ERDF in lower-$z$ quasars hosted by star forming galaxies follows a Schechter shape, 
\citep{2015MNRAS.447.2085S,2016ApJ...826...12J,2018MNRAS.474.1225A}.
Motivated by those facts, we give the ERDF by a Schechter function with two free parameters $\lambda_0$ and $\alpha$ as
%%%%%%%
%    Eq. 2
%%%%%%%
\begin{equation}
  \label{eq:Pl}
  \frac{\D P}{ \D \ln \lambda} \propto
  \left(\frac{\lambda} {\lambda_0} \right)^\alpha \exp{\left(-\frac{\lambda}{\lambda_0}\right)}.
\end{equation}
The normalization is set so that the integrant of this function over $\lambda_\mathrm{min}(=0.01) \leq \lambda < \infty$ is unity.
%normalized by the total probability above $\lambda_\mathrm{min}$ = 0.01.
The minimum Eddington ratio $\lambda_\mathrm{min}$ is adopted from the simulated evolution of quasar luminosities 
that decrease mildly toward $\lambda \sim 0.1-0.01$ with $\lesssim$ 100 Myr after the peak activity \citep{2011ApJ...737...26N}.
Moreover, a turnover at the lowest value $\lambda\lesssim 0.01-0.001$ in the ERDF is suggested by observations \citep{2018MNRAS.474.1225A}.

To characterize the ERDF for a BH population at any time snapshot together with the episodic 
accretion pattern of individual BHs, 
we introduce a time duration of $\tlife$, during which a single value of $\lambda$ that follows 
the ERDF of Eq.~(\ref{eq:Pl}) is assigned to an accreting BH.
In this way, we give a different growth speed of a BH in every period with a duration of $\tlife$ until $z=6$ 
(the corresponding cosmic age is $t_{\rm H}\simeq 800$ Myr).
This treatment enables us to capture the nature of accretion bursts and avoid an unrealistically 
long-lasting rapid growth phase of a BH.
This phenomenological method introducing a parameter of $\tlife(<t_{\rm H})$ allows us to avoid 
numerous uncertainties in modeling of the galaxy assembly, gas feeding, and BH feedback processes in the quasar 
progenitor halos.
Instead of treating those ingredients implemented in previous semi-analytical models, we extract 
an averaged but fundamental timescale that governs mutual correlation between the BHMF and QLF,
based on direct comparison to those distribution functions for observed high-$z$ quasar population.
%We leave a more detailed discussion to \S~\ref{sec:discussion}.}

@@

We describe how to calculate the time evolution of the BH mass function, 
combining the semi-analytical growth model and the ERDF (see Eqs.~\ref{eq:mdot} and \ref{eq:Pl}).
